The Error Estimate of Short-Range Force Calculation in the Inhomogeneous Molecular Systems

### 2012-07-25 shortRange.inhomo/alltext/pubilsh.pre/resubmit/lett.tex
finish response

by H. Wang, C. Sch\"uette and P. Zhang to:\\

@@

Throughout the paper, when we mention
that ``the cut-off of
the adaptive cut-off method is $r_c^\ast$'', we mean that its
control error is the maximum error of a uniform cut-off simulation
using that cut-off $r_c^\ast$.
Under this setting,  the maximum 
cut-off radius of the adaptive cut-off method is the same as,
or sometimes marginally larger  than
$r_c^\ast$ (no more than $r_c^{\textrm{\tiny{step}}}$).
We have made this point clear in the captions of Figures 5 and 6.
\\

@@

We have submitted a paper, titled ``The Numerical Accuracy of Computing
Electrostatic Interaction in the Inhomogeneous and Correlated
Molecular Systems: for the Ewald Summation, SPME and Staggered Mesh
Ewald Methods'', dealing with the Ewald type long-range
algorithms. In that paper, we concluded that the locally neutral systems
do not have the error anomaly at the interfacial regions. Since
most practical charged systems are locally neutral, we are safe and
do not need ARC (adaptive cut-off) or LFC (long-range force correction)
for the electrostatic calculation.
\\

@@

As far as we concerned, the error estimate technique and proposed
corrections can only be used to periodic systems.
We have added the following sentence to stress this point
(line 5, page 26):
\textbf{It should be noticed that the porposed error estimate and correction
methods can only be used to periodic systems.}
\\

@@

This is a very important comment, because
the cost of FFTs $O(N\log N)$ will overcome the cost of short-range
interaction $O(N)$ at some point when the system is very
big. Eventually the computationaly cost will be overwhelmed by the
FFTs as the size of the system grows to infinity.
This point should be noticed.  Fortunately, for the systems
also calculate long-range interactions, the short-range error estimate
scales the same as the Ewald type long-range algorithms.
We have added the following remarks to the paper:
(line 5 from the bottom, page 26):
\textbf{In the systems tested by the present paper, the computational
  load of the error estimate is small compared to that of the
  short-range interaction.
  However, it should be noticed that
  the cost of the error estimate scales as $\mathcal O(N\log N)$,
  which may become intractable when the $\mathcal O(N)$ scaling
  short-range system is extremely large, and eventually
  overwhelms the total computational cost as the
  system size grows to infinity.
  If the system also needs long-range electrostatic calculation
  that is usually treated by the $\mathcal O(N\log N)$ scaling
  Ewald type algorithms [22-24],
  the extra load of the error estimate is likely to be acceptable.
}

>>>>

by H. Wang, C. Sch\"utte and P. Zhang to:\\

@@

Throughout the paper, when we mention
that ``the cut-off of
the adaptive cut-off method is $r_c^\ast$'', we mean that the
control error  $\mathcal E^\ast_{\textrm{\tiny{C}}}$
is the same as the maximum error of a uniform cut-off simulation
using $r_c^\ast$.
Under this setting,  the maximum 
cut-off radius of the adaptive cut-off method is the same as,
or sometimes marginally larger  than
$r_c^\ast$ (no more than $r_c^{\textrm{\tiny{step}}}$).
We have changed the captions of Figures 5 and 6 to make it clear.
\\

@@

We  have recently submitted a paper,
titled ``The Numerical Accuracy of Computing
Electrostatic Interaction in the Inhomogeneous and Correlated
Molecular Systems: for the Ewald Summation, SPME and Staggered Mesh
Ewald Methods''.
In that paper, the error estimates for both the
direct space short-range part and the reciprocal space long-range
part are developed.
We prove that the inhomogeneity error vanishes in the
locally neutral systems, so
there is no error anomaly at the interfacial regions. Since
most practical charged systems are locally neutral,
we are basically safe and
do not need neither ARC (adaptive cut-off)
nor LFC (long-range force correction)
for the electrostatic calculation. We 
have also tested an artificial system that is NOT locally neutral. We find
the direct space error presents similar error anomaly at the interface,
while the reciprocal error (Kspace error) does not
have any anomaly.
Therefore, the reciprocal force calculation
needs no adjustment, so the reciprocal space working parameters
(interpolation order and grid spacing) and the splitting
parameter can be fixed. When these parameters are fixed, the direct
space force calculation is decoupled from the reciprocal space,
so the ARC can be applied.
\\

@@

As far as we concerned, the error estimate technique and proposed
corrections can only be used to periodic systems.
We have added the following sentence to stress this point
(line 8, page 26):
\textbf{It should be noticed that the proposed error estimate and correction
methods can only be used for periodic systems.}
\\

@@

This is a very important comment, because
the cost of FFTs ($O(N\log N)$) will overcome the cost of short-range
interaction ($O(N)$) at some point when the system is very
large. Eventually the computationally cost will be overwhelmed by the
FFTs as the size of the system grows to infinity.
This point should be noticed.  Fortunately, for the systems
also calculate long-range interactions, the short-range error estimate
scales the same as the Ewald type long-range algorithms.
We have added the following remarks to the paper
(2nd line from the bottom, page 26):
\textbf{In the systems tested by the present paper, the computational
  load of the error estimate is small compared to that of the
  short-range interaction.
  However, it should be noticed that
  the cost of the error estimate scales as $\mathcal O(N\log N)$.
  If the system only has short-range interaction that
  scales as $\mathcal O(N)$, the load of the error estimate
  may become comparatively expensive when the system is large,
  and eventually
  overwhelms the total computational cost as the
  system size grows to infinity.
  If the system also needs long-range electrostatic calculation
  that is usually treated by the $\mathcal O(N\log N)$ scaling
  Ewald type algorithms [22-24],
  the extra load of the error estimate is likely to be acceptable.
}
